TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-10 paper/paper.tex
Update paper.tex

	The created environment is shown in figure \ref{fig:setup1}.

@@

	In scenario 1 the TCP congestion algorithm is tested for fairness in sharing bandwidth with other TCP connections using other TCP congestion algorithms. In order to test the fairness of congestion algorithms, the bandwidth allocation per algorithm is measured. It can be determined whether a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more or less bandwidth to that specific TCP connection.

>>>>

	The created testing environment is shown in figure \ref{fig:setup1}. This is a virtual representation of the network as the client node and random node are running on one physical device. The client node and random node are listening each on a different port, which is set by the controller described in section [ENTER SECTION]. The servers are separate physical devices as one of the servers possible runs Windows when a TCP congestion control algorithm is only available for Windows. The software used for the servers and clients is Ubuntu 17.04. If Windows is used, the server will be running Windows 10.

@@

	In scenario 1 the TCP congestion algorithm is tested for fairness in sharing bandwidth with other TCP connections using other TCP congestion algorithms. In order to test the fairness of congestion algorithms, the bandwidth allocation per second per algorithm is measured. It can be determined whether a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more or less bandwidth to that specific TCP connection.
